API - Application Programming Interface. A set of instructions that can be used to interact with an application or module.

Bash - Short for Bourne Again Shell, Bash is a Unix shell commonly found in MacOS and Linux distrubutions.

Class - A term from object-oriented programming, a class is an extensible code template for creating objects.

Class Loader - A part of the Java Runtime Environment, the class loader is responsible for locating libraries, reading their contents, and loading the classes contained within the libraries.

Dynamic analysis - Dynamic analysis is the testing and evaluation of software during runtime

Environment - A particular configuration of hardware or software

Source code -  A collection of text written using a human-readable programming language

GUI - Graphical User Interface.

heatcode - our prototype tool for analyzing Java programs run as jar files.

IDE - Integrated Development Environment. An environment that lets developers write and run code with supporting tools to automate processes.

IntelliJ - A popular IDE for Java development by the company JetBrains

Fernflower - A decompiler for Java binaries made for the IntelliJ IDE

.jar, Java binary - A file format that aggregates Java class files and metadata in one file for distribution.

Java - a popular high-level object-oriented programming language that is architecture neutral.

JavaScript - Not to be confused with Java, a popular high-level programming language typically used for web development.

JDI - Java Debugging Interface. A high-level interface to access the state of a JVM instance. 

JDI Profiler - Our program that runs a user's jar-file, collecting information about loaded classes and methods called during run-time.

JVM - Java Virtual Machine. A specification for implementing a system-agnostic virtual machine that programs can be run on.

Lambda (expression) - An anonymous function not bound to an identifier.

Library - A collection of non-volatile resources used by computer programs.

Node.js - A back-end JavaScript runtime environment, typically used for modern web servers.

Profiling - The practice of evaluating a program based on certain characteristics.

Program - A sequence or set of instructions in a programming language for a computer to execute.

React - A JavaScript library for building declarative web applications.

Refactoring - The process of altering the internal structure of a software project without changing the external functionality.

Life-cycle, Runtime - The phase of a program in which the program is actively running

Serialization - Translating data to a format that can be persisted or transported

SourcePrinter - Our Java program that aggregates decompiled source code and method calls

Static analysis - Extracting information about a program from its source code or artifacts.

TypeScript - A statically typed programming language that transpiles to JavaScript.



Words
code base (konsistens med source code?)
source code (iflg Helge)
substring
Er special navne som f.eks. heatcode altid i kursiv? Calculator/instances?
Første gang vi nævner et program - kursiv/stort. Ellers bare stort. Metoder er kursiv.
.\{filtype\}-files!
One, two, ..., ten, 11, 12, ..., n
Chapter 5.2
JSON
runtime
amerikanske stavninger